\trtitle

### 2024-12-05 BAI/paper/presentation.tex
Added structure for BAI paper and presentation.
Added current state.

\documentclass[14pt]{beamer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Meta informations:
\newcommand{\trauthor}{Horst Hansen}
\newcommand{\trtype}{} %{Proseminar} %{Seminar} %{Workshop}
\newcommand{\trcourse}{Knowledge Processing with Neural Networks}
\newcommand{\trtitle}{Neural Networks for Artificial Agents}
\newcommand{\trmatrikelnummer}{6543210}
\newcommand{\tremail}{hansen@informatik.uni-hamburg.de}
\newcommand{\trinstitute}{Dept. Informatik -- Knowledge Technology, WTM}
\newcommand{\trwebsiteordate}{{http://www.informatik.uni-hamburg.de/WTM/}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Languages:

% Falls die Ausarbeitung in Deutsch erfolgt:
% \usepackage[german]{babel}
% \usepackage[T1]{fontenc}
% \usepackage[latin1]{inputenc}
% \usepackage[latin9]{inputenc}
% \selectlanguage{german}

% If the thesis is written in English:
\usepackage[english]{babel}
\selectlanguage{english}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bind packages:
\usepackage{beamerthemesplit}
\usetheme{Boadilla}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{Frankfurt}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Madrid}
%\usetheme{Warsaw }
%\usecolortheme{dolphin}
%\setbeamertemplate{sections/subsections in toc}[sections numbered]
%\beamertemplatenavigationsymbolsempty
%\setbeamertemplate{headline}[default] 	% deaktiviert die Kopfzeile
\setbeamertemplate{navigation symbols}{}% deaktiviert Navigationssymbole
%\useinnertheme{rounded}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Configurationen:
%\hypersetup{pdfpagemode=FullScreen}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Costom Definitions:
\setbeamertemplate{title page}
{
  \vbox{}
	\vspace{0.4cm}
  \begin{centering}
    \begin{beamercolorbox}[sep=8pt,center,colsep=-4bp]{title}
      \usebeamerfont{title}\inserttitle\par%
      \ifx\insertsubtitle\@empty%
      \else%
        \vskip0.20em%
        {\usebeamerfont{subtitle}\usebeamercolor[fg]{subtitle}\insertsubtitle\par}%
      \fi%
    \end{beamercolorbox}%
		\vskip0.4em
    \begin{beamercolorbox}[sep=8pt,center,colsep=-4bp,rounded=true,shadow=true]{author}
      \usebeamerfont{author}\insertauthor \\ \insertinstitute
    \end{beamercolorbox}

	  \vfill
	  \begin{beamercolorbox}[ht=8ex,center]{}
		  \includegraphics[width=0.20\paperwidth]{wtmIcon.pdf}
	  \end{beamercolorbox}%
    \begin{beamercolorbox}[sep=8pt,center,colsep=-4bp,rounded=true,shadow=true]{institute}
      \usebeamerfont{institute}\trwebsiteordate
    \end{beamercolorbox}
		\vspace{-0.1cm}
  \end{centering}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Additional 'theorem' and 'definition' blocks:
\newtheorem{axiom}{Axiom}[section]
%\newtheorem{axiom}{Fakt}[section]			% Wenn in Deutsch geschrieben wird.
%Usage:%\begin{axiom}[optional description]%Main part%\end{fakt}

@@

%Additional types of definitions:
\theoremstyle{remark}
%\newtheorem{remark}[section]{Bemerkung} % Wenn in Deutsch geschrieben wird.
\newtheorem{remark}[section]{Remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Provides TODOs within the margin:
\newcommand{\TODO}[1]{\marginpar{\emph{\small{{\bf TODO: } #1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abbreviations and mathematical symbols
\newcommand{\modd}{\text{ mod }}
\newcommand{\RS}{\mathbb{R}}
\newcommand{\NS}{\mathbb{N}}
\newcommand{\ZS}{\mathbb{Z}}
\newcommand{\dnormal}{\mathit{N}}
\newcommand{\duniform}{\mathit{U}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Display of TOCs:
\AtBeginSection[]
{
	\setcounter{tocdepth}{2}
	\frame
	{
	  \frametitle{Outline}
		\tableofcontents[currentsection]
	}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document:
\begin{document}
\renewcommand{\arraystretch}{1.2}

\begin{frame}[plain] % plain => kein Rahmen
  \titlepage
\end{frame}
%\setcounter{framenumber}{0}

\frame{
	\frametitle{Outline}
	\tableofcontents
}

%%%%%%%%%%%%%%
% Your Content

\section{Motivation and Question}

\frame[t]{
  \frametitle{Motivation}
  \begin{itemize}
  	\item Add your motivation here
		\begin{itemize}
			\item Maybe  with some details
			\begin{itemize}
				\item but not too much
			\end{itemize}
		\end{itemize}
		\item Use references \textsuperscript{[Author, 2010]}
	\end{itemize}
}

\section{Basics and Definition}

\section{Approach}

\section{Results}

\section{Conclusion}

\frame[t]
{
  \frametitle{Conclusion}

  Novelty and contribution of this work:
  \begin{itemize}
	  \item Sum up the approach
		\item Sum op the results
		\item ...
		\item Show that it solves the question
  \end{itemize}

\mbox{ }

	Open Questions:
  \begin{itemize}
  	\item Something
	  \item ... is always missing
  \end{itemize}
}

%%%%%%%%%%%%%%

\frame[c]{
  \frametitle{The End}
\begin{center}
  Thank you for your attention.\\[1ex]
  Any question?\\[5ex]
\end{center}
  \footnotesize
  Literature:
	\begin{itemize}
		\item Author , Author , Author, and Author. Name of the conference paper. \emph{In: Proceedings of the Conference Name}, 2008
		\item Author, Author, and Author. Name of the Article. \emph{Name of the Journal}, 42:111-133, 2010
		\item Author, and Author. \emph{Name of the Book}. Publisher, 2009
	\end{itemize}
}

>>>>

\documentclass[10pt]{beamer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Metainformation
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\trauthor}{Leopold Lemmermann}
\newcommand{\trtype}{Seminar}
\newcommand{\trcourse}{Bio-inspired Artificial Intelligence}
\newcommand{\trtitle}{Image Captioning}
\newcommand{\trmatrikelnummer}{7724741}
\newcommand{\tremail}{leopold.lemmermann@studium.uni-hamburg.de}
\newcommand{\trinstitute}{Dept. Informatik -- Knowledge Technology, WTM}
\newcommand{\trwebsiteordate}{{http://www.informatik.uni-hamburg.de/WTM/}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Languages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[english]{babel}
\selectlanguage{english}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bind packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{beamerthemesplit}
\usetheme{Boadilla}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{Frankfurt}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Madrid}
%\usetheme{Warsaw }
%\usecolortheme{dolphin}
%\setbeamertemplate{sections/subsections in toc}[sections numbered]
%\beamertemplatenavigationsymbolsempty
%\setbeamertemplate{headline}[default] 	% deaktiviert die Kopfzeile
\setbeamertemplate{navigation symbols}{}% deaktiviert Navigationssymbole
%\useinnertheme{rounded}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hypersetup{pdfpagemode=FullScreen}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Custom definitions
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setbeamertemplate{title page}
{
  \vbox{}
	\vspace{0.4cm}
  \begin{centering}
    \begin{beamercolorbox}[sep=8pt,center,colsep=-4bp]{title}
      \usebeamerfont{title}\inserttitle\par%
      \ifx\insertsubtitle\@empty%
      \else%
        \vskip0.20em%
        {\usebeamerfont{subtitle}\usebeamercolor[fg]{subtitle}\insertsubtitle\par}%
      \fi%
    \end{beamercolorbox}%
		\vskip0.4em
    \begin{beamercolorbox}[sep=8pt,center,colsep=-4bp,rounded=true,shadow=true]{author}
      \usebeamerfont{author}\insertauthor \\ \insertinstitute
    \end{beamercolorbox}

	  \vfill
	  \begin{beamercolorbox}[ht=8ex,center]{}
		  \includegraphics[width=0.20\paperwidth]{res/wtmIcon.pdf}
	  \end{beamercolorbox}%
    \begin{beamercolorbox}[sep=8pt,center,colsep=-4bp,rounded=true,shadow=true]{institute}
      \usebeamerfont{institute}\trwebsiteordate
    \end{beamercolorbox}
		\vspace{-0.1cm}
  \end{centering}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Additional 'theorem' and 'definition' blocks
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newtheorem{axiom}{Axiom}[section]
%Usage:%\begin{axiom}[optional description]%Main part%\end{fakt}

@@

%Additional types of definitions:
\theoremstyle{remark}
\newtheorem{remark}[section]{Remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abbreviations and mathematical symbols
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\modd}{\text{ mod }}
\newcommand{\RS}{\mathbb{R}}
\newcommand{\NS}{\mathbb{N}}
\newcommand{\ZS}{\mathbb{Z}}
\newcommand{\dnormal}{\mathit{N}}
\newcommand{\duniform}{\mathit{U}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Display of TOCs:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \AtBeginSection[]
% {
% 	\setcounter{tocdepth}{2}
% 	\frame
% 	{
% 	  \frametitle{Outline}
% 		\tableofcontents[currentsection]
% 	}
% }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\renewcommand{\arraystretch}{1.2}

\begin{frame}[plain]
  \titlepage
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}
	\begin{itemize}
			\item \textbf{Image Captioning}: Generating textual descriptions for images \cite{vinyals:2015}.
			\item \textbf{Challenges}: Complex problem combining computer vision (CV) and natural language processing (NLP) \cite{xu}.
			\item \textbf{Advancements}: Deep learning models using CNNs for feature extraction and RNNs for language generation \cite{he, simonyan}.
	\end{itemize}
\end{frame}

\section{Methods}
\begin{frame}{Methods}
	\begin{itemize}
			\item \textbf{Dataset:} Flickr8k, with 8,000 images and five captions per image \cite{vinyals:2015}.
			\item \textbf{Architecture:} Encoder-Decoder architecture:
					\begin{itemize}
							\item Encoder: CNN-based (ResNet-50, VGG-16) \cite{he, simonyan}.
							\item Decoder: RNN-based (GRU, LSTM) \cite{hochreiter}.
					\end{itemize}
			\item \textbf{Evaluation Metrics:} BLEU score for performance \cite{papineni}, with CIDEr as an alternative \cite{vedantam}.
	\end{itemize}
\end{frame}

\section{Approach}
\begin{frame}{Approach}
	\begin{itemize}
			\item \textbf{Data Preprocessing:} Resize images, normalize, and tokenize captions \cite{vinyals:2015}.
			\item \textbf{Model Training:} Train decoder using Adam optimizer and monitor BLEU score for validation \cite{papineni}.
			\item \textbf{Model Evaluation:} Evaluate BLEU score after each epoch for overfitting assessment \cite{rennie}.
	\end{itemize}
\end{frame}

\section{Results}
\begin{frame}{Results}
	\begin{itemize}
			\item BLEU scores for encoder-decoder combinations (ResNet-GRU, VGG-GRU, ResNet-LSTM, VGG-LSTM) \cite{he, simonyan}.
				\item \textbf{Best Performance:} VGG encoder with LSTM decoder, highest BLEU score in the first epoch \cite{vinyals:2015}.
				\item Observation of \textbf{Overfitting}: Decrease in BLEU scores over epochs \cite{rennie}.
	\end{itemize}
\end{frame}

\section{Conclusion}
\begin{frame}{Conclusion}
	\begin{itemize}
			\item \textbf{Summary:} VGG-LSTM model achieved the best BLEU score and stability across epochs \cite{vinyals:2016}.
			\item \textbf{Future Work:} Explore other architectures (e.g., transformers), datasets (e.g., Flickr30k, MS COCO), and metrics (e.g., CIDEr) \cite{vedantam}.
	\end{itemize}
\end{frame}

\begin{frame}[allowframebreaks]
	\bibliographystyle{apalike}
	\bibliography{bib}
\end{frame}
